`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added the convolution and inner product of two Gaussian
minor edits
edits to the discussion

This estimation framework also has theoretical implications by establishing a framework that has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models. For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}. Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond to the theoretically derived parameters where these bump solutions can exist. In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and anaesthesia.

@@

and hence completing the proof. For 3 dB attenuation at $\boldsymbol\nu_c$ we need to set

@@

where $\boldsymbol\mu=\mu_i+\mu_j$.

The inner product of two Gaussian basis functions is defined as
\begin{equation}\label{eq:InofGaussianDefinition}
\phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r
\end{equation}
A Gaussian basis function is symmetric with respect to its center, therefore
\begin{equation}\label{eq:GaussianSymmetry}
 \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r)
\end{equation}
A direct consequence of equation \ref{eq:GaussianSymmetry} is
\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
 \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r)
\end{equation}
substituting equation \ref{eq:ConsequenceofGaussianSymmetry} in equation \ref{eq:InofGaussianDefinition} we have 
\begin{eqnarray}
\phi_i\otimes\phi_j&=&\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&\int_{\mathcal R^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i)
\end{eqnarray}
from equation \ref{eq:ConvoftwoGaussianNonzeroMean} we have
\begin{equation}
 \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
\end{equation}
\section{Notation}

>>>>

The development of an estimation framework also has theoretical implications. The procedure has the potential to allow testing of hypotheses that have been generated in theoretical studies and to validate neural field models. For example, it has been hypothesised that so-called ``bump solutions'' are a possible mechanism for short term memory formation~\cite{Coombes2005}. Using the proposed model-based framework, we can reconstruct a neural field from data, and estimate parameters and check if they correspond to the theoretically derived parameters where these bump solutions can exist. In addition, the parameters and the state-space can be explored during other cognitive tasks and states of arousal such as during sleep and anaesthesia.

@@

and hence completing the derivation. For 3 dB attenuation at $\boldsymbol\nu_c$ we need to set

@@

where $\boldsymbol\mu=\boldsymbol\mu_i+\boldsymbol\mu_j$.

The inner product of two Gaussian basis functions is defined as
\begin{equation}\label{eq:InofGaussianDefinition}
\phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r
\end{equation}
A Gaussian basis function is symmetric with respect to its center, therefore
\begin{equation}\label{eq:GaussianSymmetry}
 \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r)
\end{equation}
A direct consequence of equation \ref{eq:GaussianSymmetry} is
\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
 \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r)
\end{equation}
substituting equation \ref{eq:ConsequenceofGaussianSymmetry} in equation \ref{eq:InofGaussianDefinition} we have 
\begin{eqnarray}
\phi_i\otimes\phi_j&=&\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&\int_{\mathcal R^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i)
\end{eqnarray}
evaluation equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
\begin{equation}
 \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
\end{equation}
\section{Notation}
